---
title: "Exercise 8: Practice with R Markdown"
author: "Patricia Trowbridge"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a level 2 header below in Markdown with the name "Answer 1".

# **ANSWER  LEVEL 1 IN BOLD **

## *ANSWER LEVEL 2 IN ITALICS*


2. Add an unordered Markdown list of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.


* ENCHILADAS
    + ground red chiles
    + corn tortillas
* GREEN SALAD
    + leafy vegetables
    + nuts

3. Add an R code chunk below. Show the `summary` of the `Orange` dataset. Run a
linear regression using the `lm` function to predict `circumference` from `age`
and assign the result. Show the `summary` of the fit object that you assigned. 

```{r}
data("Orange")
summary(Orange)


orange.lmfit <- lm(circumference ~ age, data = Orange)

summary(orange.lmfit)

```

4. Add a RMarkdown format link below to your favorite R reference website.


[R Cookbook link](https://r-graphics.org/)

5. Replace the author field in the `yaml` header with your name and then
successfully `knit` the RMarkdown document into a Word document.


6. Follow the instructions at https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork
to submit your assignment via GitHub to the https://github.com/CUNYSPHCode/IntroR repository.

