---
title: "Introduction to R for Data Management and Analysis"
author: "Marcel Ramos, MPH"
date: "Thursday, June 13, 2019"
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme: structureitalicserif
    theme: CambridgeUS
  ioslides_presentation: default
---

```{r setup, include = FALSE, echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
```

# Notes on last Tuesday's lecture

* Examples with pipes
* Formulas
* Aggregating
* Reshaping your data
* Downloading files from GitHub
    * Use the 'raw' button when at the page
    * Use Git GUI software
        * https://git-scm.com/download/gui/windows

# Outline for today

* Review exercises
* Combining data manipulations
* Reshaping data
* Plotting in base R
* Exploratory Data Analysis
* Intro to ggplot2
* Saving graphics

# But first, a quote...

> The data may not contain the answer. The combination of some data and an
aching desire for an answer does not ensure that a reasonable answer can be
extracted from a given body of data. -John Tukey

# Review

* Exercises
* Creating a `data.frame`

# Using the `nycflights13` dataset

```{r, echo = TRUE, message = FALSE, warning = FALSE}
library(nycflights13); library(dplyr)
flights %>% group_by(carrier) %>%
  summarise(avg_depdelay = mean(dep_delay, na.rm = TRUE),
            count = n()) %>% left_join(airlines) %>%
    arrange(avg_depdelay) %>% head
```

# Reshaping data

* Useful to prepare data for visualizations
* long vs wide
* long format - multiple observations per row (survival data)
* wide format - a single observation per row

# Reshaping data using `gather`

```{r, echo = TRUE, message = FALSE}
data(iris); library(tidyr)
longdata <- gather(tbl_df(iris), key = measure, n,
  Sepal.Length:Petal.Width) %>% separate(measure, c("type",
    "dimension"))
longdata %>% group_by(Species, type, dimension) %>%
  summarise(avg_dim = mean(n, na.rm = TRUE))
```

# Pew example

```{r, echo = TRUE}
library(readr)
(pew <- read_csv("../Data/pew.csv"))
```

# Gather dataset

```{r, echo = TRUE}
pew %>% gather(income, n, -religion) %>% head
```

income, religion : variables to gather 
n : variable in cells 
-religion means all except religion

# `group_by` operations

* Allow users to group different levels of categories of 1 or more variables
* Efficient summirization

# Using `group_by` (1)

```{r, echo = TRUE}
pew %>% gather(income, n, -religion) %>%
  group_by(income) %>% summarise(totals = sum(n))
```

# Using `group_by` (2)

```{r, echo = TRUE}
pew %>% gather(income, n, -religion) %>%
  group_by(religion) %>% summarise(totals = sum(n))
```

# Plotting and Graphing

* Exploratory Data Analysis
* Base R graphics
* Intro `ggplot2`
* Saving graphics

# Plotting systems in R

* 'Base' graphics
* lattice
* ggplot2 

# Exploratory Data Analysis

* Informal representation data
* Looking for patterns, outliers, etc.
* Get familiar with your data!

# Types of graphs

* Historgram
* Scatterplot
    * Scatterplot matrix
* Boxplots / dotplots (`ggplot2`)
* Violin plots (`ggplot2`)
* Q-Q plots
* Mosaic plots
* and many more!

# `par` function

* Check parameters for graphing
* Allows you to control the finer details of plotting

# `ggplot2` - Grammar of Graphics

* Different syntax
    * Slight learning curve
* Plots are built in layers
* Operations add layers to the plot

# Saving outputs

* Common formats for saving plots:
    * PDF
    * SVG
    * PNG/TIFF
* but there are more

End in `dev.off()` for closing the graphics window

`ggplot2` graphics may require a `print` before it gets rendered in the
file. 

# Recommended resources

* [Fundamentals of Data Visualization](https://serialmentor.com/dataviz/)
    * Claus O. Wilke
* [R Graphics Cookbook](http://www.cookbook-r.com/Graphs/)
    * Winston Chang
