---
title: "Introduction to R for Data Management and Analysis"
author: "Marcel Ramos"
date: "Tuesday, June 21, 2018"
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme: structureitalicserif
    theme: CambridgeUS
  ioslides_presentation: default
---

```{r setup, include = FALSE, echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
```

# Announcements

* Exercises mostly graded
* Extra credit due Thursday
* Final class today

# Notes on Tuesday's lecture

* Questions on the material

*\large{Pseudocode}*
\normalsize{}

* `for` loop structure
```{r, eval=FALSE, echo=TRUE}
for (variable in vector) {
    # < enter code here > 
} 
```
* `function` structure
```{r, eval = FALSE, echo=TRUE}
functionname <- function(argument1 = "default",
                         argument2 = "default") {
    myresult <- anotherfunction(argument1, argument2)
        return(myresult)
}
```

# Notes on Tuesday's lecture

* Functions are powerful tools
* Minimize errors
* Create a set of operations to achieve a goal
* Easy to write
* Loops are useful but are not easily extendable

# Data Analysis

* R is particularly good at statistics
* Packages with new methods get published faster
* Extensibility is an advantage compared to other software

# The basics

* Frequency tables
* Calculating odds ratios
* `relevel`

# Frequencies

* `gmodels` package
* `CrossTable` function
* `table` function

# Tests

* `chisq.test` function
* `fisher.test` function
* `t.test` function

# Useful functions to apply on model objects

* Functions that work on `lm` class objects
    * `summary`
    * `fitted`
    * `resid`
    * `predict`

# Tidy model results with *broom*

* `tidy` - model coefficients
* `augment` - fitted/residual values and more
* `glance` - model level statistics

# Linear Regression

* `lm` function
* [\color{blue}{UCLA example}](http://scc.stat.ucla.edu/page_attachments/0000/0139/reg_1.pdf)

# Logistic Regression and Odds Ratios

* `glm` function
* `Odds Ratio` calculation
* [\color{blue}{UCLA example}](http://www.ats.ucla.edu/stat/r/dae/logit.htm)

