---
title: "R Exercises Session 2"
author: "Introduction to R for Data Management and Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note**: Use `Ctrl (Command) + Alt (Option) + I` or go to `Code` >
`Insert Chunk` (from the menu) to insert a code block "chunk".

## Exercises

1. Look at the documentation for the `rep` function.
**Note:** Before writing anything in the console, try to guess on paper what the
function call will look like.

Now, use the `rep` function to output the following vectors to the R console:

a) 6, 6, 6, 6, 6
b) 3, 2, 3, 2, 3, 2, 3, 2
c) 7, 7, 7, 7, 9, 9, 9, 9

---

```{r}
## Enter answers for 1 in this chunk
rep(6, 5)
rep(c(3,2), 4)

rep(c(7,9), each = 4)

# also accepted:
c(rep(7, 4), rep(9, 4))
```


2. Write a character vector with your 3 favorite food items and assign it to an
object called `myFaves`.

```{r}
myFaves <- c("sushi", "ramen", "soba")
```

3. Create a factor from the `myFaves` character vector.

```{r}
factor(myFaves)
```


4. Create an ordered factor from the `myFaves` character vector by arranging the
levels argument in the proper order.

```{r}
myFaves <- factor(myFaves, levels = c("soba", "sushi", "ramen"), ordered = TRUE)
myFaves
```

5. Load the `mtcars` dataset by running the `data()` function on it. How many
columns does the data have? How many rows? What function do you use to look at
the car makes and models?

```{r}
data(mtcars)
ncol(mtcars)
nrow(mtcars)
rownames(mtcars)
```

6. Use a series of **20** random numbers with a mean of **20** and a standard
deviation of **5** to create a matrix with **4** rows.

```{r}
matrix(data = rnorm(n = 20, mean = 20, sd = 5), nrow = 4)
```

7. Create a list of 2 vectors (a character vector of a, b, and c and a numeric
vector of one to ten) with names `element1` and `element2`.

```{r}
list(element1 = c("a", "b", "c"), element2 = 1:10)
```

