---
title: "R Exercises Session 6"
author: "Introduction to R for Data Management and Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercises

1. You are tasked to test whether there is a difference in mean miles per gallon
(`mpg`) by type of motor (`vs`) (v-shape or straight). Run a t-test on the
variables in question. What is the result? Show another way to calculate the
mean by group. What type of motor has a higher mean miles per gallon? Show your
code.

```{r}

```

2. Fit a linear model with the `Orange` dataset. You are investigating how age
relates to circumference of a tree. Use the `predict` function to estimate the
circumference of a `500` day old tree. Show your code.

```{r}

```

3. Using what you learned, load the `babies.txt` dataset and set values of '9'
to missing in the smoking variable (`smoke`). Run a t-test to see if the average
birth weight (`bwt`) is significantly different between mothers who smoke and
those who don't.

```{r}

```

4. Run a linear regression with `gestation`, `smoke`, `age` as predictors of
birth weight `bwt`. Create a plot of fitted vs residual values using the
functions learned in class.

```{r}

```

## Extra Credit 

5. Using the `lm` object in #4, create a table (`data.frame`) of beta ($\beta$)
coefficients using the `coef` function on the `summary` of the model. Add
columns for confidence intervals with `confint`.

```{r}

```

