---
title: "R Exercises Session 5"
author: "Introduction to R for Data Management and Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note**: Use `Ctrl (Command) + Alt (Option) + I` or go to `Code` >
`Insert Chunk` (from the menu) to insert a code block "chunk".

## Exercises

1. Write a simple function that takes a number as an input and raises it to the
power of `3`. Name this function `cube`. See `?Arithmetic`.

```{r}

```

2. Create a `4` by `5` matrix of random numbers using `rnorm` and assign it.
Write a `for` loop that takes the `sum` of each of the rows and returns a
vector of row sums.

```{r}

```

3. Use `split` to divide `mtcars` by `am` type and assign the output to a
variable. Now use an `lapply` function with `dim` as a functional argument.
What are the dims in each dataset?

```{r}

```

4. Write a function with an argument called "directory" that counts the number
of "csv" files in that directory. (hint: see the `list.files` function)

```{r}

```


5. Use a `tapply` function to take the average weight of chicks in `chickwts` in
each of the feed categories.

```{r}

```


## Extra Credit

6. Use `vapply` to check whether all the columns in the `mtcars` dataset are
numeric. Include the `X`, `FUN` and the `FUN.VALUE` arguments.

```{r}

```

