---
title: "R Exercises Session 8"
author: "Professor Ramos (ANSWER KEY)"
date: "Thursday, June 28, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a `Header2` header below with the name "Answer 1".

## Answer 1


2. Add an unordered list of your favorite food dishes and add their ingredients
as sub-items in the list. You should enter at least two dishes with two
ingredients each.

* onigiri
    * rice
    * tuna
* pizza
    * mozzarella
    * soppressata

3. Add a code chunk below. Show the `summary` of the `Orange` dataset. Run a
linear regression using the `lm` function to predict `circumference` from `age`
and assign the result. Show the `summary` of the fit object that you assigned. 

```{r}
data(Orange)

summary(Orange)

ofit <- lm(circumference ~ age, data = Orange)

summary(ofit)
```

4. Add a link below (_in RMarkdown format_) to your favorite R reference website.

[R For Data Science](http://r4ds.had.co.nz/)

5. Replace the author field in the `yaml` header with your name and `knit` the
RMarkdown document into a Word document and submit via Blackboard. Make sure
that the document runs **without** errors.
