---
title: "R Exercises Session 2"
author: "Introduction to R for Data Management and Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note**: Use `Ctrl (Command) + Alt (Option) + I` or go to `Code` >
`Insert Chunk` (from the menu) to insert a code block "chunk". 

## Exercises

1. Look at the documentation for the `rep` function. 
**Note:** Before writing anything in the console, try to guess on paper what the
function call will look like.

Now, use the `rep` function to output the following vectors to the R console:

a) 6, 6, 6, 6, 6
b) 3, 2, 3, 2, 3, 2, 3, 2
c) 7, 7, 7, 7, 9, 9, 9, 9

---

```{r}
## Enter answers for 1 in this chunk
```


2. Write a character vector with your 3 favorite food items and assign it to an
object called `myFaves`.

```{r}

```

3. Create a factor from the `myFaves` character vector. 

```{r}

```

4. Create an ordered factor from the `myFaves` character vector (with the
`ordered` argument) by arranging the levels argument in the order from _least_
to _greatest_ in personal preference.

```{r}

```

5. Load the `mtcars` dataset by running the `data()` function on it, i.e.,
`data("mtcars")`.

How many columns does the data have?

```{r}

```

How many rows?

```{r}

```

What function do you use to look at the car makes and models?

```{r}

```

6. Create a series of **20** random numbers with a mean of **20** and a standard
deviation of **5** using the `rnorm` function and then create a matrix with
**4** rows.

```{r}

```

7. Create a `list` of 2 vectors (a character vector of letters a, b, and c and a
numeric vector from one to ten) with names `element1` and `element2`.

```{r}

```

