---
title: "R Exercises Session 3"
author: "Introduction to R for Data Management and Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note**: Use `Ctrl (Command) + Alt (Option) + I` or go to `Code` >
`Insert Chunk` (from the menu) to insert a code block "chunk".

## Exercises

1. Load the `iris` dataset using `data`. Take only the observations that have a
`Petal.Width` greater than `2.0`.
Show your code. 

```{r}

```

2. Save the previous operation to an R object and use it to count the number of
each `Species` with the `table` function.

```{r}

```

3. Load the `mtcars` dataset. Extract the 'hp' variable and use the `order` function
on the vector.

```{r}

```

4. Take the mean of 'hp' and the mean of 'disp' or displacement. Which mean is higher? Show your code.

```{r}

```

5. Consider a systematic error for the weight scale used in the `ChickWeight`
dataset as obtained via the `data` function. The reading on each of the weights
was consistently 5 grams lower than the actual weight. Create a new variable
to adjust for the measurement error. Show your work.

```{r}

```

6. Read in the `babies.txt` dataset in the Example data folder using the
`read.table` function with headers enabled. For those observations that are `9`
in the `smoke` variable, replace them with `NA`. To do that, first use the `==`
operator to find observations equal to `9` in the smoke variable and then subset
the smoke vector restricted to those observations and at the same time assign
`NA` values to it. Show your work. If your assignment fails, re-import the data
to get a clean dataset.

```{r}

```

