---
title: "R Exercises Session 5"
author: "Introduction to R for Data Management and Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note**: Use `Ctrl (Command) + Alt (Option) + I` or go to `Code` >
`Insert Chunk` (from the menu) to insert a code block "chunk".

## Exercises

1. Write a small function that takes a number as an input and raises it to the
power of `3`. Name this function `cube`. See `?Arithmetic`.

```{r}
cube <- function(number) {
    number^3
}
# You can test by calling the function
cube(2)
```

2. Create a `4` by `5` matrix of random numbers using `rnorm` and assign it.
Write a `for` loop that takes the `sum` of each of the rows and returns a
vector of row sums.

```{r}
mat <- matrix(rnorm(20), nrow = 4, ncol = 5)

sumROW <- rep(0, 4)

for (i in seq_len(nrow(mat))) {
   sumROW[i] <- sum(mat[i, ])
}
## Check the operation worked, you should get a vector of length 4 (for each
## row in the matrix)
sumROW

## Verify your work using the rowSums() function
rowSums(mat)
```

3. Use `split` to divide `mtcars` by `am` type and assign the output to a
variable. Now use an `lapply` function with `dim` as a functional argument.
What are the dims in each dataset?

```{r}
split_mtcars <- split(mtcars, mtcars$am)
lapply(split_mtcars, dim)
```

4. Write a function with an argument called "directory" that counts the number
of "csv" files in that directory. (hint: see the `list.files` function)

```{r}
csv_counter <- function(directory) {
    fileVector <- list.files(
        path = directory, pattern = ".csv", full.names = TRUE
    )
    length(fileVector)
}
```


5. Use a `tapply` function to take the average weight of chicks in `chickwts`
in each of the feed categories.

```{r}
data("chickwts")

tapply(X = chickwts$weight, INDEX = chickwts$feed, mean)

## alternatives
library(dplyr)
chickwts %>% group_by(feed) %>% summarise(avg_wt = mean(weight))

aggregate(weight ~ feed, data = chickwts, FUN = mean)
```


## Extra Credit

6. Use `vapply` to check whether all the columns in the `mtcars` dataset are
numeric. Include the `X`, `FUN` and the `FUN.VALUE` arguments.

```{r}
vapply(X = mtcars, FUN = is.numeric, FUN.VALUE = logical(1L))

## alternatives
vapply(X = mtcars, FUN = is.numeric, FUN.VALUE = TRUE)
vapply(X = mtcars, FUN = is.numeric, FUN.VALUE = FALSE)
```

