---
title: "R Exercises Session 7"
author: "Introduction to R for Data Management and Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercises

1. Take the `pew.csv` dataset and reshape it to get a tally of the number of
participants by religous affiliation.

```{r}

```

2. Use the `nycflights13` package to add columns to the `flights` dataset from
the `airports` dataset. Add two columns named `origin_name` and `dest_name`
that map correctly by the airport code `faa` and return the airport name.
Use the columns `origin` and destination (`dest`) from flights to do the
mapping.

```{r}

```

3. Add a new column to your dataset recoding the `month` variable to a factor
variable. Use the internal R vector `month.name` for your labels.

```{r}

```

4. What month and airport has the most flights?

```{r}

```

5. What is the average, minimum, and maximum yearly temperatures for all listed
airports in the `weather` dataset?

```{r}

```

