---
title: "R Exercises Session 8"
author: Leen Feliciano
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a level 2 header below in Markdown with the name "Answer 1".

# Session 8 R Markdown
## Answer 1

2. Add an unordered Markdown list of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.

### My favorite foods and their ingredients
*Chocolate Banana Nice Cream
  * 2 cups vanilla soymilk
  * 2-4 ripe bananas
  * 2 tsps Hersheys unsweetened chocolate powder
  * 1 scoop garden of life chocolate protein powder
  * Ghirardelli Intense Dark 72% Cacao squares crumbled
*Mangu with Red Onion and Salami
  * ripe and green plantains
  * cold water
  * margarine or butter to taste
  * salt to taste
  * red onion sauteed in apple cider vinegar
  * salami cut into thin slices and fried in oil or butter
* Homemade Super Salad
  * 1 cup mushrooms cut in quarters
  * 1/2 can of black beans
  * 1 cup red, green, and yellow peppers diced 
  * 1/4 onion
  * 1 tsp garlic
  * chicken bouillon powder to taste
  * 1 head of lettuce
  * 2 or more cups of spinach
  * 1 whole avocado 
  * 2 hardboiled eggs
* Tuna Fish Sandwich
  * 2 slices whole grain bread with seeds
  * 1 can white albacore tuna in water
  * 1-2 tsp apple cider vinegar
  * pinch of minced garlic if desired
  * 6-8 manzanilla olives
  * mayonnaise to taste
  * salt to taste

3. Add an R code chunk below. Show the `summary` of the `Orange` dataset. Run a
linear regression using the `lm` function to predict `circumference` from `age`
and assign the result. Show the `summary` of the fit object that you assigned. 

```{r}
summary (Orange)

fit_1 <- lm(circumference ~ age, data = Orange)

summary(fit_1)

```


4. Add a RMarkdown format link below to your favorite R reference website.

[My Fave R Reference Website](https://github.com/CUNYSPHCode/IntroR)

5. Replace the author field in the `yaml` header with your name and then
successfully `knit` the RMarkdown document into a Word document.

---
title: "R Exercises Session 8"
author: Leen Feliciano
output: html_document
---


6. Follow the instructions at https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork
to submit your assignment via GitHub to the https://github.com/CUNYSPHCode/IntroR repository.

