---
title: "R Exercises Session 8"
author: "Rosio Ramos"
date: "Tuesday, June 23, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a `Header2` header below with the name "Answer 1".

## **Answer 1**

2. Add an unordered list (in Markdown syntax) of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.

* Tacos
  * tortilla
  * meat
  * salsa
  * cilantro
  * onions

* Noodles
  * carrots
  * chicken
  * ginger
  * soy sauce

* Watercress salad
  * watercress
  * been sprouts
  * potatoes
  * olive oil
  * salt
  * pepper



3. Add an R code chunk below. Show the `summary` of the `Orange` dataset. Run a
linear regression using the `lm` function to predict `circumference` from `age`
and assign the result. Show the `summary` of the fit object that you assigned. 
```{r}
data(Orange)
summary(Orange)
orange.lm <- lm(circumference ~ age, data = Orange)
summary(orange.lm)
residuals(orange.lm)
plot(fitted(orange.lm), residuals(orange.lm))
```

4. Add a link below (_in RMarkdown format_) to your favorite R reference website.

[Favorite R reference](http://www.cookbook-r.com)

5. Replace the author field in the `yaml` header with your name and `knit` the
RMarkdown document into a Word document (make sure that the document 'knits').
First clone the `CUNYSPHcode/IntroR_FinalAssignment` onto your GitHub account.
Then, create a pull request on GitHub with the **modified** RMarkdown file. 

6. Follow the instructions at https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork to submit your assignment via GitHub to the https://github.com/CUNYSPHCode/IntroR repository.
