---
title: "R Exercises Session 4"
author: "Introduction to R for Data Management and Analysis"
date: "June 14, 2016"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note**: Use `Ctrl (Command) + Alt (Option) + I` or go to `Code` > `Insert Chunk` (from the menu) to insert a code block "chunk". 

## Exercises

1. Create a histogram of the `mtcars` dataset with the `mpg` variable. Change the _x axis_ label to "Miles per Gallon (mpg)".

```{r}

```

2. Use the `mtcars` dataset to draw a scatterplot of weight `wt` and displacement `disp`. Draw a fit line using the `lm` function and formula notation. 

```{r}

```

3. Run the "pairs.panels" function from the `psych` package on the `mtcars` dataset. What variables are highly correlated (> |.80|)? What does it tell you about the displacement variable and the number of cylinders? 

```{r}

```

4. Create any 4 plots and put them in one single output device using the `par` function. Can you reorder the plots so that you get 4 in one column? Show your code. 

```{r}

```

5. Use the `iris` dataset to draw boxplots of `Petal.Length` for each of the species. Show your code. 

```{r}

```

