---
title: "R Exercises Session 8"
author: "Caroline Sheehan"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a level 2 header below in Markdown with the name "Answer 1".

## Answer 1

2. Add an unordered Markdown list of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.

* Peanut noodles
  + Buckwheat noodles
  + Peanut butter
  + Soy sauce
  + Cucumbers
  
* Birthday cake
    + Flour
    + Sugar
    + Eggs
    + Chocolate

3. Add an R code chunk below. Show the `summary` of the `Orange` dataset. Run a
linear regression using the `lm` function to predict `circumference` from `age`
and assign the result. Show the `summary` of the fit object that you assigned. 

```{r}
summary(Orange)

model <- lm(circumference~age, Orange)

summary(model)
```

4. Add a RMarkdown format link below to your favorite R reference website.

[R For Data Science](https://r4ds.had.co.nz/index.html)

5. Replace the author field in the `yaml` header with your name and then
successfully `knit` the RMarkdown document into a Word document.


6. Follow the instructions at https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork
to submit your assignment via GitHub to the https://github.com/CUNYSPHCode/IntroR repository.

